An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-01 poly-embed-journal/poly-embed-journal.tex
Mid meeting

\section{General characteristics of polyhedra}
\jessiet{replace G with $\hyp g$ and $g := g_\V$
	break C.1.1 into its own subsection - make sure everything is completely self-contained with general functions}
\subsection{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $(w,b) \in \reals^d \times \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$. 
\end{definition}
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$.
\end{definition} 
Observe that the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.

@@

%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}
\jessiet{Revisit: definition of hyperplanes is not oriented}
\begin{definition}[Supports]
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
\end{definition}

\begin{definition}[Face, facet]
  Let $P \subseteq \reals^d$ be a convex polyhedron.
  A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
  A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
  \begin{equation*}
    F_{(w,b)} = P \cap H_{(w,b)}~,~
  \end{equation*}
  for any valid halfspace $H^+_{(w,b)}$.
  The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
  A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.
\end{definition}

@@

	It is just left to show (ii).
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
	Thus, $F_{(w,b)}$ is a facet of $P$, and is of dimension $d-1$.
	This implies the facet $F_{(w,b)}$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H_{(w,b)}$.
	As halfspaces are uniquely determined, so is the facet $F_{(w,b)} = P \cap H_{(w,b)}$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H_{(w,b)} \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

	%A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
	%As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.

  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

@@

\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
%\begin{claim}
%	$\H_{\V^*} \subseteq \H$
%\end{claim}
%\begin{proof}
%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.  Or re-work this proof.}
%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
%	Thus, we must have $\H_{v^*} \subseteq \H$.
%\end{proof}

>>>>

\section{General characteristics of polyhedra}
\subsection{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $(w,b) \in \reals^d \times \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ be the closed halfspace defined by $(w,b)$. 
\end{definition}
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^d \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ be the hyperplane generated by $(w,b)$.
\end{definition} 
Observe that the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.

@@

\jessie{Add notation for halfspaces that are not oriented; say $H'$ is a halfspace of $H$}

%\raf{Maybe add def supporting hyperplane; cor of face def is that nonempty face iff supporting hyperplane}

\jessiet{Revisit: definition of hyperplanes is not oriented}
\begin{definition}[Supports]
	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	(i) $P \subseteq H^+$ or $P \subseteq -H^+$, and
	(ii)$H \cap \mathrm{bd}(P) \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \mathrm{bd}(P)$.
\end{definition}

\jessie{In definition 19, need a way to go uniquely from halfspace to hyperplane}

\begin{definition}[Face, facet]
  Let $P \subseteq \reals^d$ be a convex polyhedron.

  A \emph{face} $F$ of the polytope $P$ is any set of the form
  \begin{equation*}
    F = P \cap H~,
  \end{equation*}
  for any valid halfspace $H^+_{(w,b)}$.
  The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
  A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.

%Let $P \subseteq \reals^d$ be a convex polyhedron.
%A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
%% A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
%A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
%\begin{equation*}
%F_{(w,b)} = P \cap H_{(w,b)}~,~
%\end{equation*}
%for any valid halfspace $H^+_{(w,b)}$.
%The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
%A face $F$ with $\dim(F) = \dim(\affhull(P)) - 1$ is called a facet.

\end{definition}

@@

	It is just left to show (ii).
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that each $H^+_{(w,b)} \in \H^*$ uniquely determines a facet of $P$.
	Thus, $F_{(w,b)}$ is a facet of $P$, and is of dimension $d-1$.
	This implies the facet $F_{(w,b)}$ can be defined by $d$ affinely independent points (contained in $P$), whose affine hull is $H_{(w,b)}$.
	As halfspaces are uniquely determined, so is the facet $F_{(w,b)} = P \cap H_{(w,b)}$.
	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem), we must have $H^+_{(w,b)} \in \H^*$. 
	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

%  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

@@

\btw{Commented out a claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
%\begin{claim}
%	$\H_{\V^*} \subseteq \H$
%\end{claim}
%\begin{proof}
%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.  Or re-work this proof.}
%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
%	Thus, we must have $\H_{v^*} \subseteq \H$.
%\end{proof}
